---
title: "Cifti MSC Analysis"
author: "Tahia Warda"
date: "2023-05-18"
output: html_document
---

```{r}
install.packages("rprojroot")
install.packages("tidyverse")
install.packages("caret")
install.packages("readr")
install.packages("ggplot2")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(caret)
library(readr)
library(ggplot2)
library(ciftiTools)
ciftiTools.setOption('wb_path', './bin_windows64/wb_command.exe')
library(R.matlab)
library(fpc)
```

```{r}
subj <- ciftiTools::read_cifti(paste0("../data/surface_pipeline/sub-MSC06/processed_task_timecourses/ses-func01/sub-MSC06_ses-func01_task-memory_bold_32k_fsLR.dtseries.nii"))
surfL <- ciftiTools::read_surf(surf = "../data/surface_pipeline/sub-MSC06/fs_LR_Talairach/fsaverage_LR32k/MSC06.L.inflated.32k_fs_LR.surf.gii", expected_hemisphere = "left")
surfR <- ciftiTools::read_surf(surf = "../data/surface_pipeline/sub-MSC06/fs_LR_Talairach/fsaverage_LR32k/MSC06.R.inflated.32k_fs_LR.surf.gii", expected_hemisphere = "right")
subj <- ciftiTools::add_surf(subj, surfL, surfR)
```

to csv files
```{r}
for (i in 6:8){
  for (j in 1:2){
    subj <- ciftiTools::read_cifti(paste0("../data/surface_pipeline/sub-MSC0",i,
                                          "/processed_task_timecourses/ses-func0",j,
                                          "/sub-MSC0",i,"_ses-func0",j,
                                          "_task-memory_bold_32k_fsLR.dtseries.nii"))
    subjL <- subj$data$cortex_left %>% as_tibble()
    write.csv(subjL, file=paste0("./msc0",i,"_sess0",j,"_L_dts.csv"), row.names=FALSE, col.names=FALSE)
    
  }
  
}
```


trying to get first difference of scan timeseries
```{r}
msc1.diff <- matrix(0,dim(msc1$data$cortex_left)[1], 
                    dim(msc1$data$cortex_left)[2]-1)

for (i in seq(dim(msc1$data$cortex_left)[2]-1)){
  msc1.diff[,i] = msc1$data$cortex_left[,i] - msc1$data$cortex_left[,i+1]
}
```

now, is there any correlation between them?  actually, let's break 'em down into little bits of 10.
```{r}
msc1.bits <- tibble(time=seq(10))

for (i in seq(dim(msc1.diff)[1])){
  for (j in seq(dim(msc1.diff)[2])-9){
    msc1.bits <- msc1.bits %>% 
      add_column(!! paste0("voxel_",i,"_timestep_",j) := msc1.diff[i,j:j+9])
  }
}
saveRDS(msc1.bits, file = "msc01_lagged_times.rds")
```

```{r}
msc1_main.bits <- tibble(time=seq(10))

for (i in seq(dim(msc1$data$cortex_left)[1])){
  for (j in seq(dim(msc1$data$cortex_left)[2])-9){
    msc1_main.bits <- msc1_main.bits %>% 
      add_column(!! paste0("voxel_",i,"_timestep_",j) := msc1$data$cortex_left[i,j:j+9])
  }
}
saveRDS(msc1_main.bits, file = "msc01_lagged_times_main.rds")
```


```{r}
time_lagger <- function(vxl){
  
  v <- msc1$data$cortex_left[vxl,]
  d <- length(v)
  expd <- d-(d%%10)
  vmat <- matrix(0,10,(expd^2)+expd)

  for (j in seq(d-9)){
      vmat[,j] <- v[j:(j+9)]
  }
  
  return(vmat)
}
```

```{r}
voxels <- seq(dim(msc1$data$cortex_left)[1]) %>% as.list()
msc1.mat <- sapply(voxels, time_lagger)
#saveRDS(msc1.bits, file = "msc01_mat_left.rds")
```


```{r}
voxels <- seq(dim(msc1$data$cortex_left)[1]) %>% as.list()
diff.mat <- sapply(voxels, function(x) sapply(msc1.diff[x,], time_lagger))
saveRDS(msc1.bits, file = "msc01_mat_diff1.rds")
```


Let's see where these bits are:
```{r}

for (i in 6:8){
  
  # Initialize palette
  pal <- topo.colors(401)
  rgbpal <- col2rgb(pal) / 255
  r <- rgbpal[1,]
  g <- rgbpal[2,]
  b <- rgbpal[3,]
  Alpha <- rep(1, length(401))

  # Read in the data
  # subj <- ciftiTools::read_cifti(paste0("../data/surface_pipeline/sub-MSC0",i,
  #                                       "/processed_task_timecourses/ses-func0",j,
  #                                       "/sub-MSC0",i,"_ses-func0",j,
  #                                       "_task-memory_bold_32k_fsLR.dtseries.nii"))
  gmhbm <- R.matlab::readMat(paste0("./5_sess/beta50/Ind_parcellation_MSHBM_sub",i-5,"_w20_MRF20_beta50.mat"))
  surfR <- ciftiTools::read_surf(surf = paste0("../data/surface_pipeline/sub-MSC0",i,"/fs_LR_Talairach/fsaverage_LR32k/MSC0",i,".R.inflated.32k_fs_LR.surf.gii"), expected_hemisphere = "right")
  surfL <- ciftiTools::read_surf(surf = paste0("../data/surface_pipeline/sub-MSC0",i,"/fs_LR_Talairach/fsaverage_LR32k/MSC0",i,".L.inflated.32k_fs_LR.surf.gii"), expected_hemisphere = "left")
  # subj <- ciftiTools::add_surf(subj, surfL, surfR)
  
  # Create color code
  tmp <- gmhbm$lh.labels
  tmp <- append(tmp, gmhbm$rh.labels)
  Key <- sort(unique(tmp))

  # set up the labels
  p <- ciftiTools::load_parc("Yeo_17")
  p$data$cortex_left <- gmhbm$lh.labels
  p$data$cortex_right <- gmhbm$rh.labels
  p$surf$cortex_left <- surfL
  p$surf$cortex_right <- surfR
  
  # Let's see where everything is
  for (k in Key){
    k <- k+1
    Red <- rep(0,length(Key))
    Blue <- rep(0,length(Key))
    Green <- rep(0,length(Key))
    Red[[k]] <- r[[k]]
    Green[[k]] <- g[[k]]
    Blue[[k]] <- b[[k]]
    p$meta$cifti$labels$parcels <- data.frame(Key, 
                                              Red, Green, 
                                              Blue, Alpha)
    ciftiTools::write_cifti(p, cifti_fname = paste0("./sub-MSC0",i,
                                                    "_rukong_parcel_",
                                                    k,
                                                    ".dlabel.nii"))
  }
}

```

```{r}
# Initialize palette
pal <- topo.colors(401)
rgbpal <- col2rgb(pal) / 255
r <- rgbpal[1,]
g <- rgbpal[2,]
b <- rgbpal[3,]
Alpha <- rep(1, length(401))

for (i in 6:8){

  # Read in the data
  # subj <- ciftiTools::read_cifti(paste0("../data/surface_pipeline/sub-MSC0",i,
  #                                       "/processed_task_timecourses/ses-func0",j,
  #                                       "/sub-MSC0",i,"_ses-func0",j,
  #                                       "_task-memory_bold_32k_fsLR.dtseries.nii"))
  gmhbm <- R.matlab::readMat(paste0("./5_sess/beta50/Ind_parcellation_MSHBM_sub",i-5,"_w20_MRF20_beta50.mat"))
  surfR <- ciftiTools::read_surf(surf = paste0("../data/surface_pipeline/sub-MSC0",i,"/fs_LR_Talairach/fsaverage_LR32k/MSC0",i,".R.inflated.32k_fs_LR.surf.gii"), expected_hemisphere = "right")
  surfL <- ciftiTools::read_surf(surf = paste0("../data/surface_pipeline/sub-MSC0",i,"/fs_LR_Talairach/fsaverage_LR32k/MSC0",i,".L.inflated.32k_fs_LR.surf.gii"), expected_hemisphere = "left")
  # subj <- ciftiTools::add_surf(subj, surfL, surfR)
  
  # Create color code
  tmp <- gmhbm$lh.labels
  tmp <- append(tmp, gmhbm$rh.labels)
  Key <- sort(unique(tmp))

  # set up the labels
  p <- ciftiTools::load_parc("Yeo_17")
  p$data$cortex_left <- gmhbm$lh.labels
  p$data$cortex_right <- gmhbm$rh.labels
  p$surf$cortex_left <- surfL
  p$surf$cortex_right <- surfR
  
  # Let's see where everything is

  Red <- rgbpal[1,]
  Blue <- rgbpal[3,]
  Green <- rgbpal[2,]

  p$meta$cifti$labels$parcels <- data.frame(Key, 
                                            Red, Green, 
                                            Blue, Alpha)
  ciftiTools::write_cifti(p, cifti_fname = paste0("./sub-MSC0",i,
                                                  "_rukong_parcel_.dlabel.nii"))

}

```



```{r}
p <- ciftiTools::read_xifti("./sub-MSC06_rukong_parcel_.dlabel.nii")
surfR <- ciftiTools::read_surf(surf = paste0("../data/surface_pipeline/sub-MSC06/fs_LR_Talairach/fsaverage_LR32k/MSC06.R.inflated.32k_fs_LR.surf.gii"), expected_hemisphere = "right")
surfL <- ciftiTools::read_surf(surf = paste0("../data/surface_pipeline/sub-MSC06/fs_LR_Talairach/fsaverage_LR32k/MSC06.L.inflated.32k_fs_LR.surf.gii"), expected_hemisphere = "left")

p$surf$cortex_left <- surfL
p$surf$cortex_right <- surfR
```

Make ids of the voxels. (one hopes)
```{r}
idxs <- list()
for (i in c(36, 187, 198, 199, 190, 201)){
  tmp <- list()
  for (j in seq(29162)){
    if (subj6_resamp$data$cortex_left[j]==i){
      tmp <- append(tmp, j)
    }
  idxs <- append(idxs, tmp)
  }
}
```
parallel version of above
```{r}
n.cores <- parallel::detectCores() - 1
#create the cluster
clustmsc <- parallel::makeCluster(
  n.cores, 
  type = "PSOCK"
  )

doParallel::registerDoParallel(cl = clustmsc)
```

Let's get the voxels that fit the parcels of interest
```{r}
ROI <- foreach(i = c(125, 36, 187, 198, 199, 190, 201)
                    ) %:%
                      foreach(j=1:32492
                      ) %dopar% {
                        if (gmhbm$lh.labels[j]==i){
                          if (j %in% medial_wall){
                            j
                            }
                          }
                        }

parallel::stopCluster(cl = clustmsc)
```

```{r}
names(ROI) <- c("p125", "p36", "p187", "p198", "p190", "p199", "p201")
for (i in names(ROI)){
  print(length(ROI[[i]]))
}
```


```{r}
for (i in names(ROI)){
  ROI[[i]][sapply(ROI[[i]], is.null)] <- NULL
}
```


Create matrix:
```{r}
for (i in 6:8){
  for (j in 1:2){
    subj <- ciftiTools::read_cifti(paste0("../data/surface_pipeline/sub-MSC0",i,
                                          "/processed_task_timecourses/ses-func0",j,
                                          "/sub-MSC0",i,"_ses-func0",j,
                                          "_task-memory_bold_32k_fsLR.dtseries.nii"))
    for (n in names(voxl)){
      parcvox <- subj$data$cortex_left[unlist(ROI[[n]]),]
      hmat <- matrix(0, ncol=length(parcvox), nrow=length(parcvox))
      for (row in seq(dim(parcvox)[1])){
        for (col in seq(dim(parcvox)[1])){
          hmat[i,j] <- cor(parcvox[i,], parcvox[j,], method="pearson")
        }
      }
      write.csv(hmat, file = "./msc06_p125_corr_mat.csv", sep = ',', col.names = TRUE)
    } 
```

```{r}
#automatic install of packages if they are not installed already
list.of.packages <- c(
  "foreach",
  "doParallel",
  "ranger",
  "palmerpenguins",
  "tidyverse",
  "kableExtra"
  )

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]

if(length(new.packages) > 0){
  install.packages(new.packages, dep=TRUE)
}

#loading packages
for(package.i in list.of.packages){
  suppressPackageStartupMessages(
    library(
      package.i, 
      character.only = TRUE
      )
    )
}
```



# get_voxels <- function(ind_parc, subj){
#   # We have vertex numbers, but we need to
#   # get the voxels for those vertices
#   parc_rois <- c(125, 36, 187, 198, 199, 190, 201)
#   
#   parc_names <- c("p125", "p36", "p187", "p198", "p190", "p199", "p201")
#   
#   roi_voxls <- foreach(i = parc_rois
#   ) %:% {
#     roi <- get_parcel_verts(ind_parc, i)
#   }
#   
#     foreach(j = 1:length(subj6$meta$cortex$medial_wall_mask$left)
#     ) %dopar% {
#       if (j %in% roi){
#         if (j %in% cortL_vertices){
#           j
#         }
#       }
#     }
#   names(roi_voxls) <- parc_names
# 
# }
```{r}
# Initialize palette
pal <- hcl.colors(401, palette="Cyan-Magenta")
rgbpal <- col2rgb(pal)/255
r <- rgbpal[1,]
g <- rgbpal[2,]
b <- rgbpal[3,]
Alpha <- rep(1, length(401))


# Create color code
tmp <- surfL_w_label$data$cortex_left
tmp <- append(tmp, surfL_w_label$data$cortex_right)
Key <- sort(unique(tmp))

# Let's see where everything is

Red <- rgbpal[1,]
Blue <- rgbpal[3,]
Green <- rgbpal[2,]

surfL_w_label$meta$cifti$labels$parcels <- data.frame(Key, 
                                          Red, Green, 
                                            Blue, Alpha)


```


Let's try to visualize this better:
```{r}
library(foreach)
library(parallel)

```

```{r}
n.cores <- parallel::detectCores() - 1
#create the cluster
clustmsc <- parallel::makeCluster(
  n.cores, 
  type = "PSOCK"
  )

doParallel::registerDoParallel(cl = clustmsc)
```

```{r}
roi <- c(125,36,187,199,198,190,201)

roil <- list()
for (i in 1:length(roi)){
  tmp <- which(surf_copy$data$cortex_left==roi[i])
  roil[[paste0("lp",roi[i])]] <- tmp
}

        # ) %dopar% {
        #   if (surf_copy$data$cortex_left[i] %in% roi){
        #     print(surf_copy$data$cortex_left[i])
        #     }
        #   else{
        #     surf_copy$data$cortex_left[i] <- 1
        #   }
        #   
        #   if (surf_copy$data$cortex_right[i] %in% roi){
        #     print(surf_copy$data$cortex_right[i])
        #   }
        #   else{
        #     surf_copy$data$cortex_right[i] <- 1
        #   }
        # }

```



```{r}
parallel::stopCluster(cl = clustmsc)
```

```{r}
surf_copy$data$cortex_left <- rep(1, 
                                  length(surf_copy$data$cortex_left))
surf_copy$data$cortex_right <- rep(1, 
                                  length(surf_copy$data$cortex_right))
for (i in 1:length(roi)){
  voxls <- as.numeric(unlist(roil[[paste0("lp",roi[i])]]))
  surf_copy$data$cortex_left[voxls] <- i+1
}
surf_copy$meta$cifti$labels$parcels <- data.frame(Key = seq(1,8), Red = rgbpal[1,], Green = rgbpal[2,], Blue = rgbpal[3,], Alpha = rep(1,8))
```


2024: Figuring out if I understood what I did

DIANA (divisive clustering)
```{R}
library(cluster)
mtxs <- list(lp125=matrix(rep(0,363*141), nrow=363, ncol=141),
             lp36=matrix(rep(0,363*151), nrow=363, ncol=151),
             lp187=matrix(rep(0,363*158), nrow=363, ncol=158),
             lp199=matrix(rep(0,363*121), nrow=363, ncol=121),
             lp198=matrix(rep(0,363*159), nrow=363, ncol=159),
             lp190=matrix(rep(0,363*172), nrow=363, ncol=172),
             lp201=matrix(rep(0,363*109), nrow=363, ncol=109)
             );
```

```{R}
library(cluster)
mtxs <- list(lp125=matrix(rep(0,363*141), ncol=363, nrow=141),
             lp36=matrix(rep(0,363*151), ncol=363, nrow=151),
             lp187=matrix(rep(0,363*158), ncol=363, nrow=158),
             lp199=matrix(rep(0,363*121), ncol=363, nrow=121),
             lp198=matrix(rep(0,363*159), ncol=363, nrow=159),
             lp190=matrix(rep(0,363*172), ncol=363, nrow=172)
             );
```

```{R}
for (i in 1:length(roil)) {
  # first we shape this thing into a proper matrix
  p_i_voxl <- roil[names(roil)[i]][[1]]

  for (j in 1:length(p_i_voxl)) {
    voxl <- subj$data$cortex_left[p_i_voxl[j],];
    mtxs[[names(roil)[i]]][j,] <- voxl;
  }
}

```

```{r}
# entire visual ROI
vxl_visual <- c(roil$lp125, roil$lp36, roil$lp187);

mtxs.v <- matrix(rep(0,363*450), ncol=363, nrow=length(vxl_visual));

for (i in 1:length(vxl_visual)) {
  mtxs.v[i,] <- subj$data$cortex_left[vxl_visual[i],]
}
```



```{r}
library(readr)

# msc06, sess01
msc06_sess01_p36 <- read_csv(
  "voxels/msc06_sess01_ind_parc_p36.csv"
  )

msc06_sess01_p125 <- read_csv(
  "voxels/msc06_sess01_ind_parc_p125.csv"
  )

msc06_sess01_p187 <- read_csv(
  "voxels/msc06_sess01_ind_parc_p187.csv"
  )

msc06_sess01_p199 <- read_csv(
  "voxels/msc06_sess01_ind_parc_p199.csv"
  )

msc06_sess01_p198 <- read_csv(
  "voxels/msc06_sess01_ind_parc_p198.csv"
  )

msc06_sess01_p190 <- read_csv(
  "voxels/msc06_sess01_ind_parc_p190.csv"
  )

# msc06, sess02
msc06_sess02_p36 <- read_csv(
  "voxels/msc06_sess02_ind_parc_p36.csv"
  )

msc06_sess02_p125 <- read_csv(
  "voxels/msc06_sess02_ind_parc_p125.csv"
  )

msc06_sess02_p187 <- read_csv(
  "voxels/msc06_sess02_ind_parc_p187.csv"
  )

msc06_sess02_p199 <- read_csv(
  "voxels/msc06_sess02_ind_parc_p199.csv"
  )

msc06_sess02_p198 <- read_csv(
  "voxels/msc06_sess02_ind_parc_p198.csv"
  )

msc06_sess02_p190 <- read_csv(
  "voxels/msc06_sess02_ind_parc_p190.csv"
  )

# msc08, sess01
msc08_sess01_p36 <- read_csv(
  "voxels/msc08_sess01_ind_parc_p36.csv"
  )

msc08_sess01_p125 <- read_csv(
  "voxels/msc08_sess01_ind_parc_p125.csv"
  )

msc08_sess01_p187 <- read_csv(
  "voxels/msc08_sess01_ind_parc_p187.csv"
  )

msc08_sess01_p199 <- read_csv(
  "voxels/msc08_sess01_ind_parc_p199.csv"
  )

msc08_sess01_p198 <- read_csv(
  "voxels/msc08_sess01_ind_parc_p198.csv"
  )

msc08_sess01_p190 <- read_csv(
  "voxels/msc08_sess01_ind_parc_p190.csv"
  )

# msc08, sess02
msc08_sess02_p36 <- read_csv(
  "voxels/msc08_sess02_ind_parc_p36.csv"
  )

msc08_sess02_p125 <- read_csv(
  "voxels/msc08_sess02_ind_parc_p125.csv"
  )

msc08_sess02_p187 <- read_csv(
  "voxels/msc08_sess02_ind_parc_p187.csv"
  )

msc08_sess02_p199 <- read_csv(
  "voxels/msc08_sess02_ind_parc_p199.csv"
  )

msc08_sess02_p198 <- read_csv(
  "voxels/msc08_sess02_ind_parc_p198.csv"
  )

msc08_sess02_p190 <- read_csv(
  "voxels/msc08_sess02_ind_parc_p190.csv"
  )
```


bootstrapping to see if valid

```{r}
#library(fpc)

# results <- clusterboot(msc06_sess02_p36, B=1000, bootmethod = "boot", clustermethod = hclustCBI, method="average", k=3, bscompare = TRUE)
msc06_sess01 <- clusterboot(msc06_sess01_p190, B=1000, bootmethod = "boot", clustermethod = hclustCBI, method="average", k=3, bscompare = TRUE)

msc06_sess02 <- clusterboot(msc06_sess02_p190, B=1000, bootmethod = "boot", clustermethod = hclustCBI, method="average", k=3, bscompare = TRUE)

msc08_sess01 <- clusterboot(msc08_sess01_p190, B=1000, bootmethod = "boot", clustermethod = hclustCBI, method="average", k=3, bscompare = TRUE)

msc08_sess02 <- clusterboot(msc08_sess02_p190, B=1000, bootmethod = "boot", clustermethod = hclustCBI, method="average", k=3, bscompare = TRUE)
```

```{r}
msc06_sess01$bootmean
msc06_sess02$bootmean
msc08_sess01$bootmean
msc08_sess02$bootmean
```
Let's plot these bad boys.
```{r}
m6.01.199 <- msc06_sess01_p199 %>% dist() %>% hclust( method="average") %>% as.dendrogram(height=2)

m6.02.199 <- msc06_sess02_p199 %>% dist() %>% hclust( method="average") %>% as.dendrogram(height=2)

m8.01.199 <- msc06_sess01_p199 %>% dist() %>% hclust( method="average") %>% as.dendrogram(height=2)

m8.02.199 <- msc06_sess02_p199 %>% dist() %>% hclust( method="average") %>% as.dendrogram(height=2)
```


loop through each for jaccard sim results
```{r}
jacc_sim <- list()
for (i in 1:7){
  current_parcel <- names(roil)[[i]]
  res <- clusterboot(mtxs[[current_parcel]], B=1000, bootmethod = "boot", clustermethod = hclustCBI, method="average", k=3, bscompare = TRUE)
  jacc_sim[[current_parcel]] <- res$bootmean
}
```

Extract voxels of interest
```{r}
m6.01.199 <- msc06_sess01_p199 %>% dist() %>% hclust(method="average") 

m6.02.199 <- msc06_sess02_p199 %>% dist() %>% hclust(method="average") 

m8.01.199 <- msc06_sess01_p199 %>% dist() %>% hclust(method="average")

m8.02.199 <- msc06_sess02_p199 %>% dist() %>% hclust(method="average") 